GO

### 2020-04-16 analysis/12_GO.Rmd
curleychampagne genes

```{r write}
write.csv(GO_DEGs, "../results/12_GO_DEGs.csv")
#write.csv(hyp, "../results/12_GO_DEGs_hyp.csv")
#write.csv(pit, "../results/12_GO_DEGs_pit.csv")
#write.csv(gon, "../results/12_GO_DEGs_gon.csv")
```

>>>>

```{r write}
#write.csv(GO_DEGs, "../results/12_GO_DEGs.csv")
#write.csv(hyp, "../results/12_GO_DEGs_hyp.csv")
#write.csv(pit, "../results/12_GO_DEGs_pit.csv")
#write.csv(gon, "../results/12_GO_DEGs_gon.csv")
```
